A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-03-16 graph_syntax.tex
a few more re-org changes.

\section{New Graph--based Syntax}
The ultimate goal of the new graph--based syntax presented here is to be able to 
fully describe the fundamental problem formulation for a complex design task, 
while still being able to accomodate the more specific case when a solution 
strategy is applied to the problem formulation. In order to achieve that goal 
the graph needs to accomodate a number of constructs from MDAO problem:

\begin{itemize}
    \item Analysis tools 
    \item Local and global variables 
    \item Information passing between analyses
    \item Coupling between analyses
    \item Design variables
    \item Objective or objectives 
    \item Local and global Constraints
    \item Iterative loops from solvers and optimizers
\end{itemize}

Beyond those basic constructs, there are also multiple three phases for a design process that 
all need to be representable with the new syntax. Firstly there is the initial problem definition
phase where the specific analysis tools and design goals are identified. At the end of this phase, 
a single formal problem formulation is selected specifying design variables, constraints, objectives, 
analysis tools, etc. Lastly some specifc procedure for solving the problem is selected, for example 
picking an MDAO optimization architecture. Using the proposed graph syntax, each of these phases 
can be represented with a related graph.

@@

We present some transformations that can be applied to transition any graph
between any two adjacent design phases. The \emph{maximal connectivity graph} 
represents the full potential of all the analysis codes being considered, i.e. 
a large set of analysis codes being considered for a given problem are included in
a graph, with all possible connections between them also present. The second graph 
is \emph{fundamental problem formulation graph}, which is the smallest possible graph 
that still fully defines a given problem formulation. Finally, a \emph{specific problem formulation} 
may be represented by including additional edges and node types to represent the 
solution strategy being employed to solve the problem.

@@

@@

\subsection{MDAO Graph Primatives}
There are three node types:  
\begin{description}
\item[variable node] represents passing of data.
\item[model node] represents the handling of data.
\item[driver node] represents constrol structures capable of managing iteration
\end{description}
There are two edge types: 
\begin{description}
\item[fixed edge] A fixed edge may never be removed from the graph.
\item[free edge] A free edge may be removed removed from the graph.
\end{description}

@@

@@

>>>>

\section{New Graph--based Syntax}
The ultimate goal of the new graph--based syntax presented here is to be able to 
fully describe the fundamental problem formulation for a complex design task, 
while still being able to accomodate the more specific case when a solution 
strategy is applied to the problem formulation. In order to achieve that goal 
the graph needs to accomodate a number of constructs from MDAO problems:

\begin{itemize}
    \item Analysis tools and connections between them
    \item Coupling between analyses
    \item Design Variable
    \item Objectives and constraints
    \item Local and global properties
\end{itemize}

Beyond those basic constructs, there are also three phases of a design process that 
all need to be representable with the new syntax. Firstly there is the initial problem definition
phase where the specific analysis tools and design goals are identified. At the end of this phase, 
a single formal problem formulation is selected specifying design variables, constraints, objectives, 
analysis tools, etc. Lastly some specifc procedure for solving the problem is selected, for example 
picking an MDAO optimization architecture. Using the proposed graph syntax, each of these phases 
can be represented with a related graph.

@@

The \emph{maximal connectivity graph} represents the first phase with all the 
analysis codes being considered with all possible connections between them also present. The second graph 
is \emph{fundamental problem formulation graph}, which is the smallest possible graph 
that still fully defines a given problem formulation. Finally, a \emph{specific problem formulation} 
may be represented by including additional edges and node types to represent the 
solution strategy being employed to solve the problem.

@@

In the following sections we present some graph theory basics, then demonstrate how to build 
the relevant MDAO constructs from the given grah primatives. Next we show how to construct 
the MCG, FPF, and SPF graphs from those constructs and demonstrate methods to transition between 
them.

@@

\subsection{MDAO Graph Primatives}
There are three node types:  
\begin{description}
\item[variable node] represents passing of data.
\item[model node] represents the handling of data.
\item[driver node] represents constrol structures capable of managing iteration
\end{description}

Only the variable node and the model node are allowed to be used in an MCG or FPF. 
All three nodes are required for any SPF. IN addition to the three node types, there 
are two edge types:

\begin{description}
\item[fixed edge] A fixed edge may never be removed from the graph.
\item[free edge] A free edge may be removed removed from the graph.
\end{description}

@@

\subsubsection{Analysis Blocks and Connections}

@@

\subsubsection{Design Variables, Objectives, and Constraints}

\subsubsection{Local vs Global}

\subsubsection{}
